---
title: "Contributions of marine capture fisheries to the domestic livelihoods and seafood consumption of Brazil Chile and Peru"
author: "Juliano Palacios Abrantes, MSc, Camila Vargas, MSc, Daniel Viana, PhD, Maria I. Rivera, MSc, Rocío López, MSc, Santiago de la Puente, MSc, Andrés M. Cisneros-Montemayor, PhD"
subtitle: "Response to Oceana Request for Proposal: Most Important Fisheries for People Study"
output:
  html_notebook: 
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: true
    number_sections: true

---

  pdf_document: default
---

```{r setup, eval=T, echo=F, warning=F,message=F}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R
# Please include any package used in your analysis

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#### Library ####
packages <- c(
  # "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "plotly",
  # "rgdal",
  # "RColorBrewer",
  "knitr",
  # "kableExtra",
  "data.table"#,
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "sp",
  # "rgdal", #Spatial analysis 
  # "tools" #Spatial analysis 
)

suppressWarnings(
  suppressMessages(
    suppressPackageStartupMessages(
    ipak(packages)
    )
  )
)

#### For all plots look alike

ggtheme_plot <- function() {
  theme(
    plot.title = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    strip.background = element_blank(),
    # strip.text       = element_text(size = base_size, face = "italic"),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1, face = "italic", size = 22),
    axis.text.y = element_text(size = 22),
    axis.title = element_text(size = 22),
    legend.key = element_rect(colour = NA, fill = NA),
    legend.position  = "top",
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 16),
    strip.text.x = element_text(size = 20, colour = "darkgrey")
  )
}

```

# Project Goal
Determine the contribution of specific fisheries to domestic fish consumption and domestic
livelihoods throughout Brazil, Chile, and Peru.

# Key Objectives

- Critical analysis highlighting important capture fisheries for domestic food security, in the context
of vulnerable populations and regions.
- Determine most important capture fisheries for food provision, and domestic seafood consumption
patterns through time and space.
- Determine most important capture fisheries and fisheries sectors for regional employment and
income.
- Determine most important capture fisheries and fisheries sectors for domestic catch and landed
value.

Deliverables
- Final report including a critical analysis of domestic seafood consumption, related fisheries
employment and income, and general fishery conditions of each nation included (Brazil, Chile and
Peru).
- National datasets and associated R-script, properly documented for replicating analyses and results.
- Summary of key uncertainties, data gaps and priority areas for future research and policy.

# Excecutive Summary

# Introduction

Latin American nations include the main fisheries regions of the world in terms of landings and, with a high (51%) proportion of net seafood production traded locally1, domestic fisheries remain highly important for national food security. The UN Food and Agriculture Organization estimates that Latin American countries consumed around 6.2 million tons of fish in 2015, averaging a per capita food fish consumption of 9.8 kg/year. The contribution of fisheries’ to food security and livelihoods is particularly pertinent given the ongoing World Trade Negotiations on fishery subsidies disciplines, as these are partially intended to avoid trade and operational distortions that may threaten local food security in maritime nations.

In 2016, total fish landings in Chile and Peru, two of the world’s top fishing nations, averaged 8 million tons per year [@Fishstat]. In Peru, the seafood sector generates over US 1.7 billion per year, supporting over 200 thousand jobs3. Moreover, Chile’s aquaculture production is among the largest of the world1 and fish meal and salmon exports generate over US$2.2 billion per year4. Despite comparatively lower catches, Brazil’s fisheries sustain thousands of local families in coastal areas5-6, and inland captures are among the largest of the world1. In Latin America size matters as 90% of Landings from small scale fisheries (SSF) are paramount in Latin America, as 90% of all motorized fishing vessels are under 12m
length1. However, this sector is among the most marginalized groups in the region 7, despite it being critical to achieving Sustainable Development Goal 1, “Eradicating hunger,” as highlighted by the recent FAO small scale fisheries guidelines that explicitly links the sector with food security and poverty eradication [@Fishstat].

Given the increasing pressures on vulnerable populations, including climate change but also rapid policy and market shifts, it is imperative to highlight the critical importance of particular capture fisheries for meeting domestic seafood supply. This knowledge can help guide future policies to ensure economic development does not jeopardize health and livelihoods in (particularly coastal) communities.

## Specifics Brazil
## Specifics Chile
## Specifics Peru
# Methods

The objective of this project, for each nation considered, was to determine the domestic seafood consumption (regionally, as possible) and its relationship with local employment in wild capture fisheries. Given that seafood is a widely traded commodity and that aquaculture has steadily increased supply into markets, meeting this objective will involve using species-specific data on domestic catches, aquaculture, and seafood imports and exports in order to highlight the most important species and fisheries for contributing to local and national food security.

Figure 1 below is a conceptual diagram of the anticipated methods to be undertaken in each nation. These methods directly link to the objectives proposed in the project Terms of Reference. Given the nature of fisheries data and governance systems, we anticipate that each of the nations considered will present unique challenges. Nevertheless, the overall approach (as captured in Fig. 1) will be used to maintain consistency in methods and comparability of results across nations, of course acknowledging specific uncertainties as appropriate.

Based on the best available data in each country, total seafood supply will be estimated as the sum of per-species production of domestic catch and aquaculture (minus exports), plus the sum of species specific net imports. Catch statistics will also be broken down by sectors whenever possible, including artisanal, industrial, and subsistence catches. In the case of domestic catch, inputs to aquaculture are subtracted from production (similar to exports); this is anticipated to be particularly relevant for large industrialized fisheries for small pelagics that are almost entirely reduced into fish feeds for aquaculture. The distribution of consumption (demand) of this seafood supply will be based on regional (as available) estimates of seafood consumption per capita and regional populations. An important additional aspect for the critical analysis portion of the project will be to link these regions with available socioeconomic and governance indicators, providing a basis for discussing relative vulnerabilities to potential
changes in seafood supply.

## International Analysis

The first approach that we did was to determine domestic seafood consumption, and its relationship with local employment in wild capture fisheries from international databases. While this first step represents the most broad analysis, it gives an idea of general country-level trends as well as information available to focus at more specific levels.

### Databases

The international analysis done using three main datasets. 

1. The Sea Around Us Dataset (SAU) has reconstructed fisheries catches for all three countries dating from 1950 to 2014. These data present a more accurate and complete picture of global fisheries than nationally collected data (nor the FAO dataset) [@Zeller2016]. 
2. The United Nations Come-trade database (UNCD) is managed by the Trade Statistics Branch of the United Nations Statistics Division. The UNCD has detailed trade data by commodity or services category for both merchandise trade and trade in services from 1962 to 2017 (https://unstats.un.org/unsd/trade/default.asp). 
3. Fish consumption (TBD)

### Analysis

For the former analysis we used the SAU database to estimate the total landings (tons) of Chile, Brasil, and Peru in 2014, the last year of data in the SAU database. All fishing sectors were aggregated (Industrial, Subsistence and Artisanal) and ** COMMENT: "Recreational" was ignored as it does not contribute to local food security.** Other countries that fish within Chile, Peru and Brasil were also not included in the analysis for the same reason. Landings were grouped by taxa excluding those not identified (e.g. "Marine fishes not identified"). We used the same database and method to estimate the revenue (US dollars) from each fishery. 

In addition to the landings data, we used the UNCD database to determine the value (US dollars) of fish and crustaceans, mollusks and other aquatic invertebrates imported and exported by Brazil, Chile and Peru in 2014. We estimate the net trade (*NT*) as follows:

$$NT = (E-I)-RI$$
where *E* is exports, *I* is imports and *RI* is re-imports. Due to the lack of detail in the UNCD database, all taxa in the SAU database had to be combined. Therefore, the estimate of total revenue from fisheries-related products per country in 2014 is an addition of the total landings revenue (all species) and the UN net trade.

Finally, for estimating the contribution of landings and imports to domestic seafood consumption, we used the FAO data on food security per capita...


## Brazil Specifics
## Chile Specifics
## Peru Specifics
# Results
## International

Results from the international analysis shows a clear dominance in fisheries landings of both Chile and Peru over Brazil, even thou Brazil captures around 3 times more species than the formers. In terms of total fishing revenue, all nations are simliar (**Table XX**)

```{r Total_Table, eval =T, echo = F}

#For dynamic plot
# #Data Path
Data_Path <- "./clean_databases/International/"
# # File name
SAU_F_Name <- "SAU_Dataset.csv"
# #read dataset
SAU_Database <- fread(paste(Data_Path,SAU_F_Name,
                            sep = ""))

SAU_Database %>% 
  group_by(area_name,Variable) %>%
  summarise(
    "Totals" = round(sum(Value)/10000),
    "Exploited Species" = n()
  ) %>% 
  tidyr::spread(Variable,Totals)

```

When we analyze the top ten species in terms of landing volume (tons) and value (USD), we find different trends between and within countries. Brazil's most prolific fishery in 2014 was *Umbrina canosai*, a croaker fished in the southern part of the country, however, the most exploited specie (in terms of landings) was the ray-finned fish *Sardinella brasiliensis*. For Chile, the most valuable fishery was the Chilean jack mackerel *Trachurus murphyi*, just above *Engraulis ringens*, Peruvian anchoveta, who not surprisingly represents the most landed species in the country. Finally, Peru most valuable fishery in 2014 was the Peruvian scallop *Argopecten purpuratus* but like Chile, *Engraulis ringens* was the most landed species (**Fig. XX**).

```{r SAU_Landings_Data, eval = T, echo = T, warning =F, message = F, fig.height = 15, fig.width= 10, fig.cap= "Top 25 species by landings (left) and value (right)\n from the SAU dataset. Red bars repreent species not present in the other category"}

## Data ####

#For dynamic plot
# #Data Path
Data_Path <- "./clean_databases/International/"
# # File name
SAU_F_Name <- "SAU_Dataset.csv"
# #read dataset
SAU_Database <- fread(paste(Data_Path,SAU_F_Name,
                            sep = ""))

## Former Analysis ####

SAU_Database %>%
  group_by(area_name,Variable) %>%
  top_n(n = 10, wt = Value) %>%  # Top 10, change if interactive plot
  # Determine what species are in both "Top" categories
  group_by(area_name,scientific_name) %>%  
  mutate(Repeated = n()) %>% 
  mutate(Repeated = ifelse(Repeated == 1, "No", "Yes")) %>% 
  # Plot 
  ggplot(.,
         aes(
           x= reorder(scientific_name,-Value),
           y = Value/1000, #thousands
           fill = Repeated
         )
  ) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =c("darkred",
                              "darkgreen"),
                    name ="Repeated") +
  facet_wrap(~area_name + Variable,
             scales = "free",
             ncol = 2) +
  labs(#title="Top 25 species by landings (left) and value (right)\n from the SAU dataset",
    x ="Species",
    y = "Values (Thousand of Tonns & Thousand of US Dollars)"
  ) +
  ggtheme_plot()


# For interactive plot
# Name the plot and then call it
# ggplotly(g_plot)
```

## Results Brazil
### Domestic Fish Consumption (General)
### Employment and Income (General)
### Fisheries Context (General)
## Results Chile
### Domestic Fish Consumption (General)
### Employment and Income (General)
### Fisheries Context (General)
## Results Peru
### Domestic Fish Consumption (General)
### Employment and Income (General)
### Fisheries Context (General)
# Critical Analysis 
## Overall of the region
### Brazil
### Chile
### Peru
# Conclusions
# References
# Data
# Supplemental Material List 

