---
title: "International Analysis"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, eval=T, echo=F, warning=F,message=F}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#### Library ####
packages <- c(
  # "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "plotly",
  "stringr",
  "rgdal",
  # "RColorBrewer",
  "knitr",
  # "kableExtra",
  "data.table",
  "ggrepel",
  # "gridExtra",
  # "ggmap",
  "broom",
  "rgeos",
  "sp",
  "rgdal", #Spatial analysis
  "tools" #Spatial analysis
)

suppressWarnings(
  suppressMessages(
    ipak(packages)
  )
)

## Set WD for markdown file 

setwd("~/Documents/Github/Oceana_LA/international")

### Set up pannel 

# Choose countries to analyze
Countries <- c("Brazil","Chile","Peru")
# Year(s) to be analized
Year_an <- 2014

```

### Landings data
- Estimate landings and revenue for each country form the Sea Around Us (http://www.seaaroundus.org/) database. 

#### Notes

- Using reconstructed catch
- Filter out external countries (China, South Korea and "unknown")
- Removed Chile's reported landings in Peruvian waters

#### Questions to discuss with the team:
- Should we remove Recreational landings? 
- Removed Chile's reported landings in Peruvian waters?

```{r SAU_Landings_Data, eval = T, echo = T, warning =F, message = F, fig.height = 15, fig.width= 10}

#Data Path
Data_Path <- "./information/raw_databases/SAU/"
# File name
SAU_F_Name <- "SAU EEZ 76,969,77,970,604,152,153,154,155 v47-0.csv"
#read dataset
SAU <- fread(paste(Data_Path,SAU_F_Name,
                   sep = ""))
# Data exploration
# names(SAU)
# head(SAU)
# unique(SAU$fishing_sector) # "Industrial"   "Subsistence"  "Artisanal"    "Recreational"

# Countries excluded from the analysis
unique(SAU$fishing_entity) # There are 29 countries fishing in these waters, fill filter them
Countries <- c("Brazil","Chile","Peru")
unique(SAU$area_name)
#Main fisheries

SAU$scientific_name <- gsub(" ", "\n",SAU$scientific_name)

# Plot <- #For dynamic plot
SAU_Clean <- # FOr saving the plot
  SAU %>% 
  filter(scientific_name != "Marine\nfishes\nnot\nidentified") %>%  #Removed but top in B and P
  filter(fishing_entity %in% Countries) %>% # Remove other fishing nations
  group_by(year,
           scientific_name, # Trade data is too generic for species details
           fishing_entity#,
           # fishing_sector # #Trade data is too generic for sector details
  ) %>%
  summarise(
    Total_tonnes = sum(tonnes),
    Landings_Value = sum(landed_value)
  ) %>%
  filter(year == Year_an) %>%  # Choose year to be analyzed
  rename(Reporter = fishing_entity) %>%  # Change name of variable to match UN trade dataset
  # filter(area_name != "Peru" | Reporter != "Chile") %>% 
  tidyr::gather("Variable","Value",4:5)  %>% 
  group_by(Reporter,Variable) %>%
  top_n(n = 10, wt = Value) %>%  # Top 10, change if interactive plot
  # Determine what species are in both "Top" categories
  group_by(Reporter,scientific_name) %>%  
  mutate(Repeated = n()) %>% 
  mutate(Repeated = ifelse(Repeated == 1, "No", "Yes"))

# Plot 
ggplot(SAU_Clean,
       aes(
         x= reorder(scientific_name,-Value),
         y = Value/1000, #thousands
         fill = Repeated
       )
) +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1,
                                   face = "italic")
  ) +
  scale_fill_manual(values =c("darkred",
                              "darkgreen"),
                    name ="Repeated") +
  facet_wrap(~Reporter + Variable,
             scales = "free",
             ncol = 2) +
  labs(title="Top 25 species by landings (left) and value (right)\n from the SAU dataset",
       x ="Species",
       y = "Values \n (Thousand of Tonns & US Dollars)"
  )


# For interactive plot
# Name the plot and then call it
# ggplotly(g_plot)


## Totals per Country ####

SAU_Tot <- SAU %>% 
  group_by(area_name,
           year,
           # scientific_name, # Trade data is too generic for species details
           fishing_entity#,
           # fishing_sector # #Trade data is too generic for sector details
  ) %>% 
  summarise(
    Total_tonnes = sum(tonnes),
    Landings_Value = sum(landed_value)
  ) %>% 
  filter(fishing_entity %in% Countries, # Remove China, Korea and unknown fishing country
         year == Year_an) %>%  # Choose year to be analyzed
  rename(Reporter = fishing_entity) %>%  # Change name of variable to match UN trade dataset
  filter(area_name != "Peru" | Reporter != "Chile") # Remove Chile report in Peruvean waters*

head(SAU_Clean)

# names(SAU_Clean)
# head(SAU_Clean)
# unique(SAU_Clean$fishing_entity)

# Clenaed!

#Write csv
# write.csv(SAU_Clean,
#           "SAU_Dataset.csv",
#           row.names = FALSE)


#### Proportion of the catch ####

Totals <- SAU %>% 
  filter(scientific_name != "Marine\nfishes\nnot\nidentified") %>%  #Removed but top in B and P
  filter(fishing_entity %in% Countries) %>% # Remove other fishing nations
  group_by(
    year,
    fishing_entity
  ) %>%
  summarise(
    Total_tonnes = sum(tonnes),
    Landings_Value = sum(landed_value)
  ) %>%
  filter(year == Year_an) %>% 
  ungroup() %>% 
  select(-year) %>% 
  tidyr::gather("Variable","Totals",2:3)

SAU_Spp <- SAU %>% 
  filter(scientific_name != "Marine\nfishes\nnot\nidentified") %>%  #Removed but top in B and P
  filter(fishing_entity %in% Countries) %>% # Remove other fishing nations
  group_by(
    year,
    scientific_name, # Trade data is too generic for species details
    fishing_entity
  ) %>%
  summarise(
    Total_tonnes = sum(tonnes),
    Landings_Value = sum(landed_value)
  ) %>%
  filter(year == Year_an) %>% 
  ungroup() %>% 
  select(-year) %>% 
  tidyr::gather("Variable","Partials",3:4) %>% 
  left_join(Totals,
            by = c("fishing_entity", "Variable")) %>% 
  mutate(
    Proportion = round((Partials/Totals)*100,2)
  ) %>% 
  group_by(fishing_entity,Variable) %>%
  top_n(n = 10, wt = Proportion) %>% 
  select(-4:-5) %>% 
  rename(Reporter = fishing_entity) %>%
  left_join(SAU_Clean,
            by = c("scientific_name","Reporter","Variable"))%>%  
  mutate(Repeated = n()) %>% 
  mutate(Repeated = ifelse(Repeated == 1, "No", "Yes"))

Prop_Total <- SAU_Spp %>% 
  group_by(Reporter,Variable) %>% 
  summarise(
    Tot_Prop = sum(Proportion),
    Location = max(Value)
  )


ggplot() +
  geom_bar(data = SAU_Spp,
           aes(
             x= reorder(scientific_name,-Value),
             y = Value/1000, #thousands
             fill = Repeated
           ),
           stat = "identity"
  ) +
  geom_label(data = SAU_Spp,
             aes(
               x = reorder(scientific_name,-Value),
               y = Value/1000,
               label = paste(as.character(Proportion),"%",sep = " ")
             )
  ) +
  geom_label(data = Prop_Total,
             aes(
               x = SAU_Spp$scientific_name[10],
               y = Location/1000,
               label = paste(as.character(Tot_Prop),"%",sep = " ")
             )
  ) +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1,
                                   face = "italic")
  ) +
  scale_fill_manual(values =c("darkred",
                              "darkgreen"),
                    name ="Repeated") +
  facet_wrap(~Reporter + Variable,
             scales = "free",
             ncol = 2) +
  labs(title="Top 25 species by landings (left) and value (right)\n from the SAU dataset",
       x ="Species",
       y = "Values \n (Thousand of Tonns & US Dollars)"
  )


```

```{r SOFIA_Data, eval = T, echo = T}

#### FAO Data ####

#Data Path
Data_Path <- "./information/raw_databases/FAO/"
# File name
FAO_F_Name <- "INPUT FAO Fishstat 2018.csv"
#read dataset
FAO <- read.csv(paste(Data_Path,FAO_F_Name,
                      sep = ""))

# head(FAO)
# names(FAO)
# unique(FAO$Country)

#### Cleaning Catch FAO data ####

# We selected Brazil, Chile and Peru landings and aquaculture and filter the data from 2010 to 2016

Clean_FAO_C <- FAO %>% 
  filter(Country %in% Countries,
         Sector != "Trade",
         Unit != "USD.1000") %>% # Select only Brazil, Chile and Peru
  group_by(Country,
         Comm.Name= Group, # Change name to match FISHMAR data
         # Environment, # NOTE: not identifying between marine/freshwater
         Sector #,
         # Trade.Flow, # No need its all Production anyway
         # Unit # Remove dollars from this database
         ) %>% 
  summarise_at(vars(matches("X201")), sum, na.rm=T) %>% # This fixes the FAO fishing area issue
  gather("Year","Value",4:10) %>% 
  spread(Sector,Value) # Spread catches and aquaculture

#### Change common name to match FISHMAR database 
Clean_FAO_C$Comm.Name <- gsub("\\b.\\b", " ",Clean_FAO_C$Comm.Name)


#### DONE CLEANING FAO CATCH DATA #

# Clean_FAO_C %>% 
#   group_by(Country,Year,Unit) %>% 
#   summarise(n()) 211 speices per country

#### Data Check METHODS ALERT ####
# Double check why are we having double values (e.g. Patagonian.grenadier in chile) #
# Beacuse of the FAO fishing area (Atlantic.Southwes and pacific.Southwest). I believe Oceana does not care about that so I'm adding it up! 

Check_Clean_FAO_C <- FAO %>% 
  filter(Country %in% Countries,
         Sector != "Trade") %>% 
  filter( Group == "Patagonian.grenadier")

#### Cleaning Trade FAO data####

# We selected Brazil, Chile and Peru landings and aquaculture and filter the data from 2010 to 2016. We then aggregated the data for each country, year, species and tradeflow. We lost the source detail (e.g. freshwater of saltwater).

Clean_FAO_T <- FAO %>% 
  filter(Country %in% Countries,
         Sector == "Trade") %>% # Select only Brazil, Chile and Peru
  select(Country,
         Group,
         Environment,
         Sector,
         Trade.Flow,
         # Unit,
         X2010:X2016) %>% 
  gather("Year","Value",6:12) %>% 
  filter(!is.na(Value)) %>%  #Removes years with no trade
  group_by(
    Country,
    Group, # NOTE: not identifying between marine/freshwater
    Year,
    # Unit,
    Trade.Flow #,
    # Sector
  ) %>% 
  summarise(Value = sum(Value)) %>% 
  filter(Trade.Flow != "Production") %>% 
  spread(Trade.Flow,Value)

names(Clean_FAO_T)

Clean_FAO_T %>% 
  group_by(Country,Year) %>% 
  summarise(n())

# Clean_FAO_C$Comm.Name <- gsub("\\b.\\b", " ",Clean_FAO_C$Comm.Name)

length(unique(Clean_FAO_T$Group))

# write.csv(Clean_FAO_T,
#           "FAO_Data.csv",
#           row.names = F)

#### Checkups ####

Clean_FAO_T %>%
  filter(Year == "X2016") %>%
  group_by(Country) %>%
  summarise(n())

# Comodities per country
# 155 Brasil
# 217 Chile-le
# 164 Peru


# head(Clean_FAO_C)
# names(Clean_FAO_C)
# unique(Clean_FAO_C$Country)
# unique(Clean_FAO_C$Sector)
# unique(Clean_FAO_C$Group)
# unique(Clean_FAO_C$Environment)


### Checking the famous NAs

Clean_FAO_T %>% 
  filter(is.na(Group))
# No NAs


#### Overall production per Sector FAO ####

Totals <- Clean_FAO_C %>% 
  group_by(Country,
           # Sector,
           Trade.Flow #,
           # Unit
           ) %>% 
  summarise(
    Mean = mean(Value, na.rm=T)) #%>% 
# filter(Unit != "Number",
#        Sector != "Trade" | Trade.Flow != "Production"
#        )#Until we figure out this

ggplot(Totals,
       aes(
         x = Sector,
         y = Mean/1000, #thousands
         fill = Trade.Flow
       )
) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Country + Unit,
             ncol = 2,
             scales = "free")


#### Per Species ####

# head(Clean_FAO_C)
# 
# Spp_FAO <- Clean_FAO_C %>% 
#   # filter(scientific_name != "Marine\nfishes\nnot\nidentified") %>%  #Removed but top in B and P
#   group_by(
#     Country,
#     Sector, # Trade data is too generic for species details
#     Group,
#     Trade.Flow,
#     Unit
#   ) %>%
#   summarise_at(vars(matches("X20")), sum, na.rm=T) %>% 
#   group_by(Country,
#            Sector,
#            # Group,
#            Trade.Flow,
#            Unit) %>%
#   # top_n(n = 10, wt = X2016) %>% 
#   filter(Unit != "Number",
#          Sector != "Trade" | Trade.Flow != "Production" #Until we figure out this
#   ) %>% 
#   select(-X2015,-X2014) %>% 
#   mutate(Year = 2016) %>% 
#   rename(Value = X2016)
# 
# 
# 
# # Are there any species in different Sectores per country?
# 
# Overlap <- Spp_FAO %>% 
#   group_by(Country,
#            Group,
#            Trade.Flow) %>%
#   summarise(n(),
#             Sectors = paste(Sector,
#                             collapse = (";"))
#   ) 

# unique(Overlap$Sectors)

# Overlap %>% 
#   filter(Sectors == "Aquaculture;Aquaculture;Capture")
# # Not realy, just 40 records out of 2000, many of them "Something.nei"
# 
# 
# #### __________Alfredo's Data__________ ####
Data_Path <- "./information/raw_databases/"

FISHMAR_F_Name <- "FISHMAR_data.csv"
#read dataset

FISHMAR <- read.csv(paste(Data_Path,FISHMAR_F_Name,
                      sep = ""))
# 
# head(FISHMAR)
# View(FISHMAR)

#### Standarizing both datasets ####
# Column names differe and in Alfredo's data the names are separated by "," and spaces while FAO have them by "."

### Cleaning FISHMAR data ####

Clean_FISHMAR <- FISHMAR

# names(Clean_FISHMAR)
# head(Clean_FISHMAR)
# head(Clean_FISHMAR$Commodity,20)
# head(FAO$Group,20)

# Rename to mach FAO data
Clean_FISHMAR <- Clean_FISHMAR %>% 
  rename(Group = Commodity)

### Just checking... ###

Clean_FISHMAR %>% 
  group_by(Country) %>% 
  summarise(n())

# Comodities per country in FISHAMR
#  Brazil 243
# Chile 407
# Peru 179

# In FAO... VERY similar... 
# 290 Brasil
# 402 Chile-le
# 244 Peru

# However... 
# #### Comparing datasets by Trade Group ####
# Alfredo's dataset only maches the FAO data in 32.24%

FAO_Trade <- Clean_FAO_T %>% 
  group_by(Group) %>% 
  summarise(n())
 
Semi_FAO_FISHMAR <- FAO_Trade %>%
  group_by(Group) %>% 
  summarise(n()) %>% 
  semi_join(Clean_FISHMAR,
            by = "Group") # 120 out of 472 comodities matched
# 
# unique(Semi_FAO_FISHMAR$Group)

# # What in FAO is NOT represented in Alfredo's data
Anti_FAO_FISHMAR <- FAO_Trade %>%
  group_by(Group) %>% 
  summarise(n()) %>% 
    anti_join(Clean_FISHMAR,
            by = "Group") # 245 of Alfredo's info are on FAO's
 
# unique(Anti_FAO_FISHMAR$Group)
length(unique(Anti_FAO_FISHMAR$Group)) # 245
 

# ### Missing Names in Alfredo's data ####
# 
# ## Manually checked those that do not match and found that Bonitos is a good example to talk to Alfredo
# 
# Boni_FAO <- Clean_FAO_C %>%
#   filter(str_detect(Group,"Bonito")) %>%
#   select(Group)
# 
# Boni_FISHMAR <- Clean_FISHMAR %>% 
#   filter(str_detect(Group,"bonito")) %>% 
#   select(Group)
# 
# Both <- data.frame(
#   FAO = unique(Boni_FAO$Group),
#   FISHMAR =unique(Boni_FISHMAR$Group)
# )
# 
# ## For example, FISHMAR has "Plain.bonito.frozen" and FAO has "Bonito.frozen" In total FISHMAR has 15 different Bonito valies, while FAO only 3...


#### Comparing datasets by Species (using common names) ####

# What in FAO is represented in Alfredo's data
# FAO_Production <- Clean_FAO_C %>% 
#   rename(Comm.Name = Group)
#   
# length(unique(FAO_Production$Comm.Name)) # 396 different procuts
# 
# Semi_FAO_FISHMAR_Spp <- FAO_Production %>% 
#   semi_join(Clean_FISHMAR,
#             by = "Comm.Name") # 124 of Alfredo's info are on FAO's
# 
# unique(Semi_FAO_FISHMAR_Spp$Comm.Name)
# length(unique(Semi_FAO_FISHMAR_Spp$Comm.Name)) # 83 different products
# 
# # Proportion of FAO explained by Alfredo's data
# 
# (83/356)*100 # only 23.31 percent 
# 
# # Whats not in there
# 
# Anti_FAO_FISHMAR_Spp <- FAO_Production %>% 
#   anti_join(Clean_FISHMAR,
#             by = "Comm.Name") # 4 of Alfredo's info are on FAO's


#### I guess we:
  # a ) Assume that whatever is not here is not tradable or...
  # b) We did our best to match trade with species (Probably better)

#### Datasets to Merge ####

# We merge the FAO Trade data with the FISHMAR trade data to know what captured species represent each trade groups...

#### Merging Catch Data ###

Catch_Data <- Clean_FAO_C %>% 
  left_join(Clean_FISHMAR,
            by = c("Comm.Name","Country")
  ) %>% 
  select(1,2,10,11,3:5) %>% 
  select(-Group) %>% # Need to remove all the duplicates
  distinct(.keep_all= TRUE)
  

#Checking catch data match #####

# sum(Catch_Data$Aquaculture, na.rm = T)/100000 # 113.5209
# sum(Catch_Data$Capture, na.rm = T)/100000 # 592.7257

# sum(Clean_FAO_C$Aquaculture, na.rm = T)/100000 # 113.5209
# sum(Clean_FAO_C$Capture, na.rm = T)/100000 # 592.7257

#  YES! 

# Catch_Data %>% 
#   anti_join(Clean_FAO_C,
#             by = "Comm.Name")
# All in! 


#### How many of the Catch Data is represented on FISHMAR data

Catch_Data %>% 
  group_by(Country,Comm.Name) %>% 
  summarise(n()) %>% 
  anti_join(
    Clean_FISHMAR,
    by = c("Comm.Name","Country")
  )

# Very few catch data is represented in FISHMAR


#  END CHECK _____________________

#### Merging Trade Data ####

# First those that are in FISHMAR


Trade_Data <- Clean_FAO_T %>% 
  left_join(Clean_FISHMAR,
            by = c("Group","Country")
  ) %>% 
  mutate(
    Sci.Name.Fbs = as.character(Sci.Name.Fb),
    Comm.Names = as.character(Comm.Name)
  ) %>% 
  mutate(
    Sci.Name.Fb = ifelse(is.na(Sci.Name.Fbs),Group,Sci.Name.Fbs),
    Comm.Name = ifelse(is.na(Comm.Names),Group,Comm.Names)
    ) %>% select(2,1,10,11,3:5) %>% 
  group_by(Country,Sci.Name.Fb,Comm.Name,Year) %>% 
  summarise_at(c("Exports","Imports"),sum, na.rm=T)

# Trade_Data_C <- Clean_FAO_T %>% 
#   left_join(Clean_FISHMAR,
#             by = c("Group","Country")
#   ) %>% 
#   filter(is.na(Comm.Name)) %>% 
#   group_by(Group) %>% 
  # summarise_at(c("Exports","Imports"),sum, na.rm=T)

  
#Checking we have all trade ####
# sum(Trade_Data$Exports, na.rm = T)/100000 # 804.019
# sum(Trade_Data$Imports, na.rm = T)/100000 # 180.539
# 
# For some reason values on original dataset are slightly smaller. I believe it is because in some cases the same exports represent different species (e.g. Cholga, Choro and Chilean mussels)
# sum(Clean_FAO_T$Exports, na.rm = T)/100000 # 746.1644
# sum(Clean_FAO_T$Imports, na.rm = T)/100000 # 177.3709
# 
# Trade_Data %>%
#   semi_join(Clean_FAO_T,
#             by = "Group") # All in there!

# But what about between datasets

# Those that are in trade dataset but not on Catch datset

# Trade_Data %>%
#   group_by(Country,Comm.Name) %>% 
#   summarise(n()) %>% 
#   anti_join(Catch_Data,
#             by = c("Country","Comm.Name")) %>% 
#   group_by(Comm.Name) %>% 
#   summarise(n()) # There are 6 common names in the Trade data that are not in the catch data

# Catch_Data %>%
#   group_by(Country,Comm.Name) %>% 
#   summarise(n()) %>% 
#   semi_join(Trade_Data,
#             by = "Comm.Name")

# There are 58 catched species not represented in the trade data-set


### Is the less data problem the Unknowns?
# YES!!!!!
# Now solve for the unknowns! 


# Data with NA
Trade_Data_NA <- Trade_Data %>% 
  filter(is.na(Comm.Name))

# Checking we're not loosing data
# Trade_Data_NA$Sci.Name.Fb <- "Unknown"
# Trade_Data_NA$Comm.Name <- "Unknown"

# Data without NA
Trade_Data_OK <- Trade_Data %>% 
  filter(!is.na(Comm.Name))

Trade_Data_B <- Trade_Data_NA %>% 
  bind_rows(Trade_Data_OK)

# Checking we're not loosing data
# sum(Trade_Data_B$Exports)/100000
# sum(Trade_Data_B$Imports)/100000
# Trade_Data <- Trade_Data_B


# Searching for the NAs


Trade_Data_C <- Clean_FAO_T %>% 
  left_join(Clean_FISHMAR,
            by = c("Group","Country")
  ) %>% 
  filter(is.na(Comm.Name)) %>% 
  group_by(Group) %>% 
  summarise_at(c("Exports","Imports"),sum, na.rm=T)

# Founde it! There are many commodities not matched


NAs_Search <- Clean_FAO_T %>% 
  anti_join(Trade_Data_C,
            by = c("Group","Country")
            )


#  END CHECK _____________________

#### Merging both Data ####


# First we merge those species in both....

Semi_Catch <- Catch_Data %>%
  semi_join(Trade_Data,
            by = c("Comm.Name","Sci.Name.Fb")
  )

Semi_Trade <- Trade_Data %>% 
  semi_join(Catch_Data,
            by = c("Comm.Name","Sci.Name.Fb")
  )

Semi_Data <- Semi_Catch %>% 
  left_join(Semi_Trade,
            by = c("Country","Comm.Name","Sci.Name.Fb","Year")
  )
# Checking we're not loosing data
# sum(Semi_Data$Exports,na.rm=T)/100000 # 127.7865
# sum(Semi_Data$Imports,na.rm=T)/100000 # 28.08

sum(Semi_Data$Capture,na.rm=T)/100000 # 156.7049

# Now we merge those species NOT in both....


Anti_Catch <- Catch_Data %>%
  anti_join(Trade_Data,
            by = c("Comm.Name","Sci.Name.Fb")
  )

Anti_Trade <- Trade_Data %>% 
  anti_join(Catch_Data,
            by = c("Comm.Name","Sci.Name.Fb")
  )

# Checking we're not loosing data
# sum(Anti_Trade$Exports, na.rm = T)/100000 # 676.2326
# sum(Anti_Trade$Imports, na.rm = T)/100000 # 152.4552

Anti_Data <- Anti_Catch %>% 
  bind_rows(Anti_Trade)

# Checking we're not loosing data
# sum(Anti_Data$Exports, na.rm = T)/100000 # 676.2326
# sum(Anti_Data$Imports, na.rm = T)/100000 # 152.4552

#### Merging both datasets... 

Clean_FAO_Data <- Semi_Data %>% 
  bind_rows(Anti_Data)

## Check all is there (#TheMomentOfTruth!)

Clean_FAO_Data %>% 
  gather("Variable","Value",5:8) %>% 
  group_by(Variable) %>% 
  summarise(sum(Value,na.rm=T)/100000)

#  Aquaculture                 113.52088
#  Capture                     592.72573
#  Exports                     804.0190
#  Imports                      180.5390

# YES! But we can't just leave them as "Unknown"...


# Use this data to merge with Tim's data


```


```{r Tim_Data, eval = T, echo = F}

### Species info name ###
# Tim only included species names and I need common names for FAO's data

#Data Path
Data_Path <- "./information/raw_databases/SAU/"
# File name
SAU_F_Name <- "SAU EEZ 76,969,77,970,604,152,153,154,155 v47-0.csv"
#read dataset
SAU_Spp <- fread(paste(Data_Path,SAU_F_Name,
                   sep = "")) %>% 
  rename(taxon_name = scientific_name) %>% 
  group_by(taxon_name,
           common_name) %>%
  summarise(n=n()) %>%
  select(-n)

# Tim's data ####
Tim_D <- fread("./information/raw_databases/SAU/Brazil-Peru-Chile Fisheries Data.csv")

# Im going to use the average DHC and IHC value of all secotrs (Artisanal/Industrial) and reporting status (official/reconstructed) I dont think it matters 


Clean_Tim <- Tim_D %>% 
  filter(year >= 2010) %>% 
  select(2,3,8:17) %>% 
  left_join(SAU_Spp,
            by = "taxon_name") %>% 
  mutate(
    Year = paste("X",year,sep="")
  ) %>% 
  group_by(
    Year,
    # Discards_rate, # They are all 0 or 1???
    Country = fishing_entity, #change names
    # Comm.Name = common_name,
    Sci.Name.Fb = taxon_name
  ) %>% 
  summarise_at(c("DHC_Use","FMFO_Use","Other_Use"),mean,na.rm=T) %>% 
  rowwise() %>% 
  mutate(
    IHC = sum(c(FMFO_Use,Other_Use),na.rm = T)
  ) %>% 
  group_by(Country, Sci.Name.Fb) %>% 
  summarise_if(is.numeric, mean, na.rm = TRUE) # Using the average from 20


Semi_FAO_Tim <- Catch_Data %>% 
  group_by(Sci.Name.Fb) %>% 
  summarise(n()) %>% 
  semi_join(Clean_Tim,
            by ="Sci.Name.Fb") # only 179...

Anti_FAO_Tim <- Catch_Data %>% 
  group_by(Sci.Name.Fb) %>% 
  summarise(n()) %>% 
  anti_join(Clean_Tim,
            by ="Sci.Name.Fb") # only 179...

# Plot discard frequencies... o and 1

Tim_D %>% 
  mutate(
    Discard_rate = Discards/sum
  ) %>% 
ggplot(.) +
  geom_histogram(
    aes(
    x = Discard_rate
  ),
  bins = 30
  )

#### Merging FAO + FISHMAR + Tim's data ####

International_data <- Clean_FAO_Data %>% 
  left_join(Clean_Tim,
            by = c("Sci.Name.Fb","Country")
  )

write.csv(
  International_data,
  "International_Data.csv",
  row.names = F)

```

```{r Spp_Data_For_Function, eval =T}

#### Dummy Variables #####


Dummy_Data <- data.frame(
  # Species = c(rep(FAO_Dummy$Group[41:50], times=3, each=1))) %>% 
  Species = c(rep(SAU_Clean$scientific_name[41:50], times=3, each=1))) %>% 
  mutate(
    Country = rep(c("Brazil","Chile", "Peru"), times=1, each=10),
    Year = 2016,
    Variable = rep(c("Tonnes","Value","Tonnes"), times=10, each=1),
    Catch = rnorm(30,2000,150),
    Discards = rnorm(30,0.2,0.1),
    Aquaculture = rnorm(30,1000,50),
    Aquaculture_processing = rnorm(30,0.2,0.5),
    Imports = rnorm(30,1000,50),
    Exports = rnorm(30,100,50),
    DHC = rnorm(30,0.5,0.1),
    Processing = rnorm(30,0.5,0.1)
  )


# 
# International_Dataset <- Final_FAO_Data %>% 
#   left_join(Clean_Tim,
#             by = c(
#               "Year",
#               "Country",
#               "Comm.Name",
#               "Sci.Name.Fb")
#             )



FAO_Dummy <- Clean_FAO_C %>% 
  gather("Year","Value",7:13) %>% 
  filter(Year == "X2014") %>% 
  group_by(
    Comm.Name = Group, # NOTE: not identifying between marine/freshwater
    Country,
    Year,
    Unit,
    # Trade.Flow,
    Sector
    ) %>% 
  summarise(Value = sum(Value)) %>% 
  spread(Sector,Value) %>% # First we split the sectors in catches, aqua and trade
  mutate(
    Discards = 0.20
  ) %>% 
  # Now we incorporate de Trade code from FISHMAR data
  left_join(FISHMAR_Merge,
            by = c("Country","Comm.Name","Year","Unit","Sci.Name.Fb")
  ) %>% 
  # Now we incorporate DHC/IHC from Tim's database
  left_join(Clean_Tim,
            by = c(
              "Year",
              "Country",
              "Comm.Name",
              "Sci.Name.Fb")
            )






```

```{r Spp_Function, eval =T}

#### Function Variables ####

# Catch = Fisheries Landings
# Dis = Discards lost at sea
# DHC = Proportion of the landings that go to direct human consumption
# PL = Proportion lost in processing DHC
# AP = Aquaculture production
# A_PL = Proportion lost in processing aquaculture (Can use same as wild fish, Muhammed pers. comm.)
# I_DHC = Imports to direct human consumtion
# Exp = Exports


corefx <- function(
  Species,
  Country,
  Catch,
  Dis,
  DHC,
  PL,
  AP,
  A_PL,
  I_DHC,
  Exp,
  Result = "T",
  n = 5
){
  
  #### Variables ####
  
  # First Step 
  TDS <- Catch*Dis #TDS (Total Discards) Discarded fish before landings
  LS <- Catch - TDS # LS Landings supply after discards at see
  
  # Second Step
  IHC <- LS * (1-DHC) # (Indirect Human Consumption) Landings supply that does NOT go to DHC
  SHC <- LS - IHC # (Supply for Human Consumption) Landings supply that goes to DHC
  
  # Third Step
  LP <- SHC * PL # Fish lost in processing 
  LHC <- SHC - LP # Final landings after processing losses 
  
  # Fourth Step (Aquaculture)
  AIHC <- AP * A_PL # (Aquaculture indirect human Consumption) Lost of aquaculture processing
  AHC <- AP - AIHC # (Aquaculture Human Consumption) Aquaculure human Consumption
  
  # Fifth Step (Trade)
  NI <- I_DHC - Exp # Net Imports
  
  
  # Final step
  NSP <- LHC + AHC + NI # (National Seafood Supply) 
  TIHC <- IHC + AIHC # Total IHC fishmeal fishoil
  
  
  #### Table option ####
  Result_Table <- data.table(
    "Specie" = Species,
    "Country" = Country,
    "Landings Food Supply" = LHC,
    "Aquaculutre Food Supply" = AHC,
    "Net Imports" = NI,
    "National Seafood Supply" = NSP
  )
  
  #### Graphic option ####
  Result_Table <- Result_Table %>% 
    gather("Variable","Value",3:6) %>%
    group_by(Country,Variable) %>% 
    top_n(n = 5, wt = Value)
  
  Plot <- Result_Table %>% 
  ggplot(.,
    aes(
      x= Specie,
      y = Value/1000,
      fill = Variable
    )
    ) +
    geom_bar(stat = "identity") +
    geom_label_repel(data = Result_Table,
              aes(
      x= Specie,
      y = (Value-(Value*.10))/1000,
      label = as.factor(round((Value-(Value*.10))/1000))
    ),
    show.legend = FALSE
    ) +
    ylab("Thousand Tonnes") +
    facet_wrap(~Country)

  # Function result ####
  if(Result == "T"){
  return(Result_Table)
  }
  
 if(Result == "P") {
  return(Plot)
}
  
} # End of function ####

#### Example for one single species

corefx(
  Species = "Julianus",
  Country = "Chile",
  Catch = 500,
  Dis = .9,
  DHC = 0.9,
  PL = 0.2,
  AP = 0,
  A_PL = 0.2,
  I_DHC = 0,
  Exp = 10,
  Result = "P",
  n = 5
)

### Example for multiple species
corefx(
  Result = "P",
  Country=Dummy_Data$Country,
  n = 5,
  Species = Dummy_Data$Species,
  Catch = Dummy_Data$Catch,
  Dis = Dummy_Data$Discards,
  DHC = Dummy_Data$DHC,
  PL = Dummy_Data$Processing,
  AP = Dummy_Data$Aquaculture,
  A_PL = Dummy_Data$Aquaculture_processing,
  I_DHC = Dummy_Data$Imports,
  Exp = Dummy_Data$Exports
)



corefx(
  Country=International_data$Country,
  Species = International_data$Comm.Name,
  Catch = International_data$Capture,
  Dis = 0.20,
  DHC = International_data$DHC_Use,
  PL = 0.20,
  AP = International_data$Aquaculture,
  A_PL = 0.20,
  I_DHC = International_data$Imports,
  Exp = International_data$Exports,
  Result = "T",
  n = 5
)

# Species,
#   Country,
#   Catch,
#   Dis,
#   DHC,
#   PL,
#   AP,
#   A_PL,
#   I_DHC,
#   Exp,
#   Result = "T",
#   n = 5


```

### Trade data
- Estimate imports and exports of fish for each country form the UN come-trade database

#### Methods Notes:

- Data set does not contain weight information, just US dollars
- "Fish and crustaceans, mollusks and other aquatic invertebrates" is the only classification for all three countries
- Exports - Imports - Re-Imports 

#### Questions to discuss with the team:
- What are "re-import"? Do we consider them? I'm assuming that they cost money to the country re-importing

```{r UN_Cometrade_Data, eval = T, echo = T, warning =F, message = F, fig.width= 10}

#File name
UN_F_Name <- "UN_Comtrade_Statistics.csv"


UN <- fread(paste(Data_Path,UN_F_Name,
                  sep = ""))

# Data exploration

# head(UN)
# names(UN)
# unique(UN$Commodity) # [1] "Fish and crustaceans, molluscs and other aquatic invertebrates
# unique(UN$Reporter) # [1] "Brazil" "Chile"  "Peru"  
# min(UN$Year) # 2013
# max(UN$Year) #2017

# max(UN$Gross_weight_kg)


# write.csv(UN_Clean,
#           "UN_Dataset.csv",
#           row.names = F)

#### Trade Graph ####

UN_Clean <-
  UN %>% 
  filter(Year == Year_an) %>% 
  group_by(Reporter,
           Trade_Flow
  ) %>% 
  summarise(
    Trade_Value = sum(Trade_Value_US, na.rm =T)
  ) %>% 
  spread(Trade_Flow,Trade_Value) %>% 
  mutate(
    Net_Trade_Value = (Export-Import),
    Net_Re_Import_value = ifelse(!is.na(`Re-Import`),(Net_Trade_Value -`Re-Import`),Net_Trade_Value)
  ) %>% 
  tidyr::gather("Action","Value",2:6) %>%
  filter(!Action %in% c("Re-Import","Net_Export_Value","Net_Re_Import_value")) %>% 
  ggplot(.,
         aes(
           x = Action,
           y = Value/1000000,
           # colour = Action
           fill = Action
         )
  ) +
  # geom_point()
  geom_bar(stat = "identity") +
  facet_wrap(~Reporter) +
  scale_fill_manual(values =c("green4", # Export
                              "red", # Import
                              "blue" # Totals
  )
  ) +
  theme_classic() +
  theme(legend.position = "top") +
  coord_flip() +
  labs(title="",
       x ="Countries",
       y = "Million US Dollars"
  )


#### Trade Graph With Landings ####


# UN_Clean <-
UN %>% 
  filter(Year == Year_an) %>% 
  group_by(Reporter,
           Trade_Flow
  ) %>% 
  summarise(
    Trade_Value = sum(Trade_Value_US, na.rm =T)
  ) %>% 
  spread(Trade_Flow,Trade_Value) %>% 
  mutate(
    Net_Trade_Value = (Export-Import),
    Net_Re_Import_value = ifelse(!is.na(`Re-Import`),(Net_Trade_Value -`Re-Import`),Net_Trade_Value)
  ) %>% 
  left_join(Totals,
            by = "Reporter") %>% 
  mutate(Fish_Industry_Total = Net_Trade_Value + Landings_Value) %>% 
  select(1:3,5,10) %>% 
  tidyr::gather("Action","Value",2:5) %>%
  ggplot(.,
         aes(
           x = Action,
           y = Value/1000000,
           # colour = Action
           fill = Action
         )
  ) +
  # geom_point()
  geom_bar(stat = "identity",
           width = 0.5 #Bar size
  ) +
  facet_wrap(~Reporter) +
  scale_fill_manual(values =c("green4", 
                              "blue", 
                              "red", 
                              "green3",
                              "skyblue"
  )
  ) +
  theme_classic() +
  theme(legend.position = "top") +
  coord_flip() +
  labs(title="",
       x ="Countries",
       y = "Million US Dollars"
  )





```

### Analysis

- Merge data-sets and estimate total tons of fish and revenue from fishing activity

#### Methods Notes

- Total fishing value + Net exportation gain

#### Questions to discuss with the team


```{r Analysis, eval = F, echo = T, warning =F, message = F}

# Merge Datasets ####

SAU_Clean %>% 
  left_join(UN_Clean,
            by = "Reporter") %>% 
  mutate(
    Total_Fishing_Value = Total_value + Net_Re_Import_value
  ) %>% 
  ggplot(.,
         aes(
           x = Reporter,
           y = Total_Fishing_Value,
           fill = Reporter
         )) +
  geom_bar(stat = "identity") +
  theme_classic()

```


### Map data SAU

```{r SAU_Map_Data, eval =T, echo = T}

#### FAO Data ####

#Data Path
Data_Path <- "./information/raw_databases/SAU/"
# File name
SAU_Space_F_Name <- "OceanaSpatialDataPeruChileBrazil.csv"
#read dataset
SAU_Spatial <- read.csv(paste(Data_Path,SAU_Space_F_Name,
                      sep = ""))


#### EEZ limits ####

path_eez_world <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/World_EEZ_v9_20161021/")
#The File
fnam_eez_world <- "eez_boundaries.shp"
#Load it!

#### Extract
eez_world <- readOGR(dsn = path_eez_world,
                     layer =file_path_sans_ext(fnam_eez_world))

Countries_Ar <- c(Countries,"Argentina")


#Subsetting South America
South_America <- eez_world[eez_world$Territory1 %in% Countries_Ar,]
unique(South_America@data$Territory1)


#### Countries shape ####

path.ne.coast <- "information/raw_databases/Spatial/TM_WORLD_BORDERS-0.3"
file_name <- "TM_WORLD_BORDERS-0.3.shp"

# Loading the shapefile:
World_Land <- readOGR(dsn = path.ne.coast, 
                      layer = file_path_sans_ext(file_name),
                      verbose = FALSE
                      )

# Central_A@data$NAME

South_Border <- c("Brazil",
                  "Peru",
                  "Chile",
                  "Argentina",
                  # "Colombia",
                  "Ecuador",
                  "Uruguay",
                  "Bolivia",
                  "Paraguay")


South_America_Land <- subset(World_Land, NAME %in% South_Border)

unique(South_America_Land@data$NAME)

# Getting Long and Lat data

Coor <- read.csv("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lat_Lon_DBEM.txt")

colnames(Coor) <- c("cell_id","Long","Lat")

# Merging datasets
SAU_Coor <- SAU_Spatial %>%
  group_by(fishing_entity_id,
           cell_id) %>% 
  summarise(sum = sum(sum,na.rm=T)) %>% 
  mutate(Log = log10(sum)) %>% 
  left_join(Coor,
            by = "cell_id")
  
  
# The actual map

# Some Zissouy collors :)
pal <- wes_palette("Zissou1", 100, type = "continuous")

Psum <- ggplot() +
  geom_tile(data = SAU_Coor,
               aes(
                 x=Long,
                 y=Lat,
                 fill = sum
               )
               ) +
  geom_polygon(data = South_America_Land,
               aes(
                 x = long,
                 y = lat,
                 group = group,
                 color = NAME
               ),
               fill = "gray",
               colour = "black"
               ) +
  geom_path(data = South_America,
       aes(
         x = long,
         y = lat,
         group = group
       )
       ) +
  # ylim(-75,5) +
  # xlim(-85,-26) +
  coord_fixed(xlim = c(-85, -26),  
              ylim = c(-60, 5), ratio = 1.2)+
  # facet_wrap(~Type,
  #            scales = "free") +
  scale_fill_gradientn("Catch",colours = pal) +
  theme_classic() +
  theme(legend.position = "bottom")
  
Plog <- ggplot() +
  geom_tile(data = SAU_Coor,
               aes(
                 x=Long,
                 y=Lat,
                 fill = Log
               )
               ) +
  geom_polygon(data = South_America_Land,
               aes(
                 x = long,
                 y = lat,
                 group = group,
                 color = NAME
               ),
               fill = "gray",
               colour = "black"
               ) +
  geom_path(data = South_America,
       aes(
         x = long,
         y = lat,
         group = group
       )
       ) +
  # ylim(-75,5) +
  # xlim(-85,-26) +
  coord_fixed(xlim = c(-85, -26),  
              ylim = c(-60, 5), ratio = 1.2)+
  # facet_wrap(~Type,
  #            scales = "free") +
  scale_fill_gradientn("Catch",colours = pal) +
  theme_classic() +
  theme(legend.position = "bottom")

gridExtra::grid.arrange(Psum,
                        Plog,
                        ncol = 2)


```
