---
title: "International Nalaysis"
output: html_notebook
---

```{r setup, eval=F, echo=F, warning=F,message=F}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#### Library ####
packages <- c(
  # "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "plotly",
  # "rgdal",
  # "RColorBrewer",
  "knitr",
  # "kableExtra",
  "data.table"#,
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "sp",
  # "rgdal", #Spatial analysis 
  # "tools" #Spatial analysis 
)

suppressWarnings(
  suppressMessages(
    ipak(packages)
    )
)

### Set up pannel 

# Choose countries to analyze
Countries <- c("Brazil","Chile","Peru")
# Year(s) to be analized
Year_an <- 2014

```

### Landings data
- Estimate landings and revenue for each country form the Sea Around Us (http://www.seaaroundus.org/) database. 

#### Notes

- Using reconstructed catch
- Filter out external countries (China, South Korea and "unknown")
- Removed Chile's reported landings in Peruvean waters

#### Questions to discuss with the team:
- Should we remove Recreational landings? 
- Removed Chile's reported landings in Peruvean waters?

```{r SAU_Landings_Data, eval = T, echo = T, warning =F, message = F}

#Data Path
Data_Path <- "./information/raw_databases/"
# File name
SAU_F_Name <- "SAU EEZ 604,152,76 v47-0.csv"
#read dataset
SAU <- fread(paste(Data_Path,SAU_F_Name,
                   sep = ""))
# Data exploration
# names(SAU)
# head(SAU)
# unique(SAU$fishing_sector) # "Industrial"   "Subsistence"  "Artisanal"    "Recreational"

# Countries excluded from the analysis
unique(SAU$fishing_entity) # There are 29 countries fishing in these waters, fill filter them

SAU_Clean <- SAU %>% 
  group_by(area_name,
           year,
           # scientific_name, # Trade data is too generic for species details
           fishing_entity#,
           # fishing_sector # #Trade data is too generic for sector details
           ) %>% 
  summarise(
    Total_tonnes = sum(tonnes),
    Total_value = sum(landed_value)
  ) %>% 
  filter(fishing_entity %in% Countries, # Remove China, Korea and unknown fishing country
         year == Year_an) %>%  # Choose year to be analyzed
  rename(Reporter = fishing_entity) %>%  # Change name of variable to match UN trade dataset
  filter(area_name != "Peru" | Reporter != "Chile") # Remove Chile report in Peruvean waters*
  
  head(SAU_Clean)

# names(SAU_Clean)
# head(SAU_Clean)
# unique(SAU_Clean$fishing_entity)

# Clenaed!

#Write csv
# write.csv(SAU_Clean,
#           "sau_clean_dataset.csv")
```
### Trade data
- Estimate imports and exports of fish for each country form the UN come-trade database

#### Methods Notes:

- Data set does not contain weight information, just US dollars
- "Fish and crustaceans, molluscs and other aquatic invertebrates" is the only clasification for all three countries
- Exports - Imports - Re-Imports 

#### Questions to discuss with the team:
- What are "re-import"? Do we consider them? I'm assuming that they cost money to the country re-importing

```{r UN_Cometrade_Data, eval = T, echo = T, warning =F, message = F}

#File name
UN_F_Name <- "UN_Comtrade_Statistics.csv"


UN <- fread(paste(Data_Path,UN_F_Name,
                   sep = ""))

# Data exploration

head(UN)
names(UN)
# unique(UN$Commodity) # [1] "Fish and crustaceans, molluscs and other aquatic invertebrates
# unique(UN$Reporter) # [1] "Brazil" "Chile"  "Peru"  
# min(UN$Year) # 2013
# max(UN$Year) #2017
max(UN$Gross_weight_kg)

UN_Clean <- UN %>% 
  filter(Year == Year_an) %>% 
  group_by(Reporter,
           Trade_Flow
           ) %>% 
  summarise(
    Trade_Value = sum(Trade_Value_US, na.rm =T)
  ) %>% 
  spread(Trade_Flow,Trade_Value) %>% 
  mutate(
    Net_Export_Value = (Export-Import),
    Net_Re_Import_value = ifelse(!is.na(`Re-Import`),(Net_Export_Value -`Re-Import`),Net_Export_Value)
  ); UN_Clean
  


```

### Analysis

- Merge datasets and estimate total tons of fish and revenue from fishing activity

#### Methods Notes

- Total fishing value + Net exportation gain

#### Questions to discuss with the team


```{r Analysis, eval = T, echo = T, warning =F, message = F}

# Merge Datasets ####

SAU_Clean %>% 
  left_join(UN_Clean,
            by = "Reporter") %>% 
  mutate(
    Total_Fishing_Value = Total_value + Net_Re_Import_value
  ) %>% 
  ggplot(.,
           aes(
             x = Reporter,
             y = Total_Fishing_Value,
             fill = Reporter
           )) +
  geom_bar(stat = "identity")

```